A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-04 paper/paper.tex
Plot plot plot
More plotting

\paragraph{Vertex and edge labels, connected} have yet to be run.

@@

@@

>>>>

\paragraph{Vertex and edge labels, undirected, connected} are in \cref{figure:33ve-connected-cumulative}.

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ve-connected-cumulative.pdf}
    \caption{MCS 33\% vertex and edge labelled undirected instances, connected, cumulative runtimes}\label{figure:33ve-connected-cumulative}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-sip-james-versus-kdown-nodes-scatter.pdf}
    \caption{SIP instances, James vs kdown, Nodes (TODO?? heatmapify this and exclude
    timeouts)}\label{figure:sip-james-versus-kdown-nodes-scatter}
\end{figure}
